Quantifying the ease of viral escape from broad and narrow antibodies to influenza hemagglutinin

### 2017-10-23 paper/manuscript.tex
some progress on Discussion

\section*{DISCUSSION}
We have quantified the ease of escape.
There are clear differences among antibodies
Stalk antibodies are harder to escape.

@@

Interesting that breadth does not directly associate with ease of escape.

Important caveat is that we are looking at the effects of single mutations in the background of A/WSN/1933.
Things could be different in other backgrounds and/or with combinations~\citep{gong2013stability,harms2014historical,starr2017alternative}.
\citet{wu2017diversity}.
Nonetheless, given that HA antigenic drift mostly involves point mutations...

>>>>

\section*{DISCUSSION}
We have quantified the effects of all single amino-acid mutations to HA on influenza virus neutralization by a collection of broad and narrow antibodies.
Our results show that the virus's inherent evolutionary capacity for escape via point mutations differs across antibodies. 
Interestingly, antibody breadth is not always an indicator of the difficulty of viral escape. 
As expected, single amino-acid mutations can make the virus completely resistant to narrow strain-specific antibodies against HA's globular head.
However, such mutations can also enable the virus to escape a broad antibody targeting HA's receptor-binding pocket, despite the fact that this antibody broadly neutralizes multiple HA subtypes.
But at least for the virus strain used here, no single mutations have a comparably large effect on neutralization by two broad antibodies targeting HA's stalk.
Therefore, these stalk antibodies are quantifiably more difficult for the virus to escape.

Although there are no large-effect escape mutations from the broad anti-stalk antibodies, there are mutations that more modestly affect neutralization.
This finding emphasizes the importance of identifying antigenic mutations in a way that accounts for effect sizes.
The classic approach for selecting escape mutations involves treating a virus stock with antibody at a saturating concentration that completely neutralizes wildtype, and looking for viral mutants that survive this treatment~\citep{yewdell1979antigenic,webster1980determination}.
There are no such single mutations for the HA and broad anti-stalk antibodies tested here, since no mutations shift the neutralization curve enough to enable a mutant to survive antibody concentrations that fully neutralize wildtype.
However, the comprehensive and sensitive nature of our approach enable us to identify a variety of mutations that have modest ($<$10-fold) effects on neutralization by even the broadest antibody.

@@

Important caveat is that we are looking at the effects of single mutations in the background of A/WSN/1933.
Things could be different in other backgrounds and/or with combinations~\citep{gong2013stability,harms2014historical,starr2017alternative}.
\citet{das2013defining}
\citet{wu2017diversity}.
Nonetheless, given that HA antigenic drift mostly involves point mutations...

Virus's potential for escape is ultimately combination of how easy plus how strong selection pressure...
